---
title: "Activity 6 - Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
library(tidymodels)
```

```{r}
resume <- read_csv("https://www.openintro.org/data/csv/resume.csv")
```

1. This is an observational study because none of the variables are controlled.

2. The variable received callback is a dummy variable where 0 indicates they didn't get a callback and 1 indicates they did.

3.

```{r}
resume_plot <- resume
```

```{r}
resume_plot$received_callback[resume$received_callback == 0] <- 'No'

resume_plot$received_callback[resume$received_callback == 1] <- 'Yes'
```


```{r}
resume_plot %>% 
  ggplot(mapping = aes(x = received_callback))+
  geom_bar()+
  labs(title = "Callback vs. No Callback for Jobs", 
       x = "",
       y = "Number of callback")
```

4.

```{r}

resume_plot %>% 
  count(received_callback) %>% 
  mutate(percent = 100 * prop.table(n))
```

5. It is way more likely that someone will not get a callback for a job than they will.

6. The probability that a random person will receive a callback is about 8%.

7. 

```{r}

odds <-  0.08 /(1 - 0.08)

odds
```

The odds that a random person will get a call back is around 9%.


| received_callback | Black        | White        |
|:------------------|:-------------|:-------------|
| No                | 93.55 (2278) | 90.35 (2200) |
| Yes               | 6.45 (157)   | 9.65 (235)   |

6. The probability that a black person will get a call back is 

```{r}

prob_black <- 157 / (2278 + 2200+ 235)

prob_black

```

```{r}

odds_black <- 0.03 / (1 - 0.03)

odds_black

```

```{r}

  # The {tidymodels} method for logistic regression requires that the response be a factor variable
  resume <- resume %>% 
    mutate(received_callback = as.factor(received_callback))

  resume_mod <- logistic_reg() %>%
    set_engine("glm") %>%
    fit(received_callback ~ race, data = resume, family = "binomial")

  tidy(resume_mod) %>% 
    knitr::kable(digits = 3)

```

8. 
$$
callbackwhite = -2.675 + 0.438 \times racewhite 
$$

9.

$$
callbackblack = -2.67
$$

10. The Log odd for a black person to be called back is

```{r}
log_odds_black <- log(0.03092784)

log_odds_black
```

11.

The log odds are the log of the odds. In order to get them back we would take the natural log of it.

```{r}
black_odds_check <- exp(log_odds_black)

black_odds_check
```

12.

```{r}

log_prob_black <- (black_odds_check) / (1 + black_odds_check)

log_prob_black

```

There is a 3% chance of a percieved black person being called back. This is the same as the probability I got above but it seems to have been rounded off.