---
title: "Activity 6 - Multinomial Logistic Regression"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
library(tidymodels)

```


```{r}
data <- read_csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/non-voters/nonvoters_data.csv")
```

```{r selecting_variables_needed}

voters <- data %>% 
  select(c("ppage","educ", "race","gender", "income_cat", "Q30", "voter_category"))
```

```{r rename_gender_to_sex}

names(voters)[names(voters) == "gender"] <- "sex"

```

1. If they chose people who had been able to four at least 4 election cycles they would be able to establish a pattern on whether or not individuals actually had a history of voting.

2. There doesn't seem to be a large difference between races and how often they vote. Although it does seem that it does seem that Hispanic and Other/Mixed are more likely to vote than black and white. When it come to age it seems that the older someone is the more likely they are to vote. They are also more likely to always vote exept for a dip in 35-49.


```{r changing_to_party_name}
voters <- voters %>%
  mutate(party = case_when(
    Q30 == 1 ~ "Republican",
    Q30 == 2 ~ "Democrat",
    Q30 == 3 ~ "Independent",    
    Q30 == 4 ~ "Other",
    Q30 == 5 ~ "Other",
    Q30 == -1 ~ "Other"
  ))
```

```{r creating_factor_for_voter_category}

voters <- voters %>% 
  mutate(voter_category = factor(voter_category, levels = c("rarely/never",
                                                            "sporadic",
                                                            "always")))
```

```{r}

voters %>% 
  ggplot(aes(y= educ, fill= voter_category))+
  geom_bar(position = "fill")

```

```{r}

voters %>% 
  ggplot(aes(y= party, fill= voter_category))+
  geom_bar(position = "fill")

```


```{r}
multi_mod <- multinom_reg() %>% 
  set_engine("nnet") %>% 
  fit(voter_category ~ ppage + educ + race + sex + income_cat, data = voters)

tidy(multi_mod) %>% 
  print(n = Inf) # This will display all rows of the tibble

multi_mod <- repair_call(multi_mod, data = voters)
```

$$
always = 1.854 + 0.061 \times ppage + -1.353 \times educHigh scool or less + \\
-0.412 \times educSome college + -0/.417 \times raceHispanic + \\
-0.683  \times raceOther/Mixed + 0.039 \times raceWhite + \\
0.211 \times sexMale + 0.067 \times income_cat40-75k + \\
0.147 \times income_cat75-125k + -0.756 \times income_catLess than 40k
$$

```{r}
voter_aug <- augment(multi_mod, new_data = voters)

voter_aug

voter_aug %>% 
  select(contains("pred"))
```

```{r}
voter_conf_mat <- voter_aug %>% 
  count(voter_category, .pred_class, .drop = FALSE)

voter_conf_mat %>% 
  pivot_wider(
    names_from = .pred_class,
    values_from = n
  )
```

```{r}
voters %>% 
  ggplot(aes(x = voter_category)) +
  geom_bar() +
  labs(
    main = "Self-reported voter category"
    )

voter_conf_mat %>% 
  ggplot(aes(x = voter_category, y = n, fill = .pred_class)) +
  geom_bar(stat = "identity") +
  labs(
    main = "Predicted vs self-reported voter category"
    )
```

5. The model predicts that people are sporadic voters the most. It also correctly identifies people who consider themselves sporadic voters the best. It greatly under predicts people who consider themselves rare/never voters. 